Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-02-07 aggregation/agg-agg.tex
Change $ to $

See Figure~\ref{fig:aggregation}e and f. At this level of aggregation, the entire dependency vector is replaced with an aggregated life cycle inventory vector $\tilde{\mathbf{b}}_x$ derived from the background LCIDB.  The reader no longer requires access to any background database to perform the computation, but all dependency information is concealed.  Again, foreground emissions are often not distinguished from the aggregation result (Figure~\ref{fig:aggregation}f).  The life cycle inventory $\tilde{\mathbf{b}}$ provides the most aggregated form of the study that can still be independently validated with an external characterization vector $\mathbf{e}$.

>>>>

See Figure~\ref{fig:aggregation}e and f. At this level of aggregation, the entire dependency vector is replaced with an aggregated life cycle inventory vector $\tilde{\mathbf{b}}_x$ derived from the background LCIDB.  The reader no longer requires access to any background database to perform the computation, but all dependency information is concealed.  Again, foreground emissions are often not distinguished from the aggregation result (Figure~\ref{fig:aggregation}f).  The life cycle inventory $\tilde{\mathbf{b}}$ provides the most aggregated form of the study that can still be independently validated with an external characterization vector $\mathbf{c}$.

### 2018-02-07 aggregation/agg-basic-lca.tex
Change $ to $

A symmetric input output table can be written as a table of coefficients, in which each column of the matrix provides a ``recipe'' for creating the corresponding commodity by consuming other commodities (and, if applicable, producing other co-products), equivalent to a ``unit process'' in ISO LCA, except that the reference flow is implicit in the column's index.  The table of coefficients, commonly known as a \textit{direct requirements matrix}, can be used to compute the output from all activities that is necessary to produce a given commodity.  That vector of outputs can then be combined with a second table of coefficients, known as an \textit{emission matrix}, that reports exchanges with the environment associated with the production of each commodity, to determine the cumulative environmental emissions associated with the production of the commodity over its life cycle.  Those emissions are individually \textit{characterized} with respect to an environmental impact category of interest, and the characterized emissions summed to report the \textit{impact score} or category indicator, which is the result of the study.  The formulation may be summarized:
\begin{equation}
s = \mathbf{e}^T \cdot B \cdot \left(I - A\right)^{-1} \cdot \mathbf{y}
\label{eqn:leontief}
\end{equation}
Here $A$ represents the direct requirements; $B$ is the emission matrix;  $\mathbf{e}$ is a column vector of characterization factors for the environmental emissions; $\mathbf{y}$ is the externally specified final demand; and $s$ is the numerical impact score or category indicator.  For simplicity, we will consider the computation of a single impact result.  However, it is straightforward to imagine the more typical case, in which $E$ is a matrix of characterization vectors, and $\mathbf{s}$ is a vector of results.  Eq.~\ref{eqn:leontief} is visualized in Figure~\ref{fig:lca}.
\input{fig_lca}

The term $(I-A)$ is equivalent to a normalized \textit{technology matrix}, and in certain cases can be computed from the difference between the supply and use tables, $(V'-U)$, with equivalent results \citep{Suh_JIE_2010}. 
The coefficient matrices $A$ (or $I-A$) and $B$ together are called a \textit{life cycle inventory database} (LCIDB), and the functional unit of a study is given by the final demand vector $\mathbf{y}$, which is the product or service whose delivery is to be assessed.\footnote{%
Differences in convention have led to both the direct requirements matrix $A$, and the technology matrix, analogous to $(I-A)$, being denoted by the same symbol in different contexts.  If the data contained in the LCIDB is sufficiently rich, either approach may be implemented with equivalent computational results.  The direct requirement formulation has the advantage of permitting iterative solution, which can dramatically reduce the computational resources required \citep{Peters_JLCA_2007}.}  Intermediate results of this computation include:
\begin{itemize}
\item $\mathbf{x} = \left(I-A\right)^{-1}\cdot\mathbf{y}$, the activity level vector;
\item $\mathbf{b} = B\cdot\mathbf{x}$, the life cycle inventory;
\item $s = \mathbf{e}^T\cdot\mathbf{b}$, the life cycle impact category indicator, the study result.
\end{itemize}

>>>>

A symmetric input output table can be written as a table of coefficients, in which each column of the matrix provides a ``recipe'' for creating the corresponding commodity by consuming other commodities (and, if applicable, producing other co-products), equivalent to a ``unit process'' in ISO LCA, except that the reference flow is implicit in the column's index.  The table of coefficients, commonly known as a \textit{direct requirements matrix}, can be used to compute the output from all activities that is necessary to produce a given commodity.  That vector of outputs can then be combined with a second table of coefficients, known as an \textit{emission matrix}, that reports exchanges with the environment associated with the production of each commodity, to determine the cumulative environmental emissions associated with the production of the commodity over its life cycle.  Those emissions are individually \textit{characterized} with respect to an environmental impact category of interest, and the characterized emissions summed to report the \textit{impact score} or category indicator, which is the result of the study.  The formulation may be summarized:
\begin{equation}
s = \mathbf{c}^T \cdot B \cdot \left(I - A\right)^{-1} \cdot \mathbf{y}
\label{eqn:leontief}
\end{equation}
Here $A$ represents the direct requirements; $B$ is the emission matrix;  $\mathbf{c}$ is a column vector of characterization factors for the environmental emissions; $\mathbf{y}$ is the externally specified final demand; and $s$ is the numerical impact score or category indicator.  For simplicity, we will consider the computation of a single impact result.  However, it is straightforward to imagine the more typical case, in which $C$ is a matrix of characterization vectors, and $\mathbf{s}$ is a vector of results.  Eq.~\ref{eqn:leontief} is visualized in Figure~\ref{fig:lca}.
\input{fig_lca}

The term $(I-A)$ is equivalent to a normalized \textit{technology matrix}, and in certain cases can be computed from the difference between the supply and use tables, $(V'-U)$, with equivalent results \citep{Suh_JIE_2010}. 
The coefficient matrices $A$ (or $I-A$) and $B$ together are called a \textit{life cycle inventory database} (LCIDB), and the functional unit of a study is given by the final demand vector $\mathbf{y}$, which is the product or service whose delivery is to be assessed.\footnote{%
Differences in convention have led to both the direct requirements matrix $A$, and the technology matrix, analogous to $(I-A)$, being denoted by the same symbol in different contexts.  If the data contained in the LCIDB is sufficiently rich, either approach may be implemented with equivalent computational results.  The direct requirement formulation has the advantage of permitting iterative solution, which can dramatically reduce the computational resources required \citep{Peters_JLCA_2007}.}  Intermediate results of this computation include:
\begin{itemize}
\item $\mathbf{x} = \left(I-A\right)^{-1}\cdot\mathbf{y}$, the activity level vector;
\item $\mathbf{b} = B\cdot\mathbf{x}$, the life cycle inventory;
\item $s = \mathbf{c}^T\cdot\mathbf{b}$, the life cycle impact category indicator, the study result.
\end{itemize}

### 2018-02-07 aggregation/agg-disclosure.tex
Change $ to $

The foreground matrix $A_f$, dependency matrix $A_d$, and foreground emission matrix $B_f$ now contain all study-specific information.  Assuming that the appropriate background LCIDB $B_x$, and the vector of characterization factors $\mathbf{e}$ (or their product $\mathbf{e}\times B_x$) are available and held in common between the author and the reader, then a disclosure that precisely describes $A_f$, $A_d$ and $B_f$ is sufficient to reproduce the study result, as formulated in Eq.~\ref{eqn:study}.  These three submatrices together can be considered a complete representation of the PSM.

\input{fig_disclosure}
Thus, the problem of how to disclose an LCA study design is reduced to the problem of how to communicate the contents of these submatrices accurately.  Recognizing that all three matrices are likely to be sparse (that is, that most of the entries are zero), the most efficient disclosure would be to only report non-zero entries.  A sparse matrix can be represented by a list of 3-tuples indicating (row, column, value) for each non-zero entry.  Thus, a formal disclosure of the PSM can be stated in six parts, including three lists of entities and three sets of data values:
\begin{enumerate}[label={\em d-\roman*}., ref={\em d-\roman*}]
\item\label{itm:fg} An ordered list of foreground nodes, beginning with the functional unit (rows/columns of $A_f$);
\item\label{itm:bg} An ordered list of background flows, each making reference to a particular background dataset (rows of $A_d$, mapping to columns of $B_x$);
\item\label{itm:em} An ordered list of exchanges with the environment (rows of $B_f$, mapping to entries in $\mathbf{e}$);
\item\label{itm:af} A set of 3-tuples for nonzero elements of $A_f$, in which the row and column are indices into Item~\ref{itm:fg};
\item\label{itm:ad} a set of 3-tuples for nonzero elements of $A_d$, in which the rows are indices into Item~\ref{itm:bg} and the columns are indices into Item~\ref{itm:fg};
\item\label{itm:bf} a set of 3-tuples for nonzero elements of $B_f$, in which the rows are indices into Item~\ref{itm:em} and the columns are indices into Item~\ref{itm:fg}.
\end{enumerate}
Each entity included in items \ref{itm:fg}--\ref{itm:em} describes a flow of some kind, and its unit of measure must be reported in the disclosure.
In both items~\ref{itm:bg} and~\ref{itm:em}, only rows containing non-zero entries need to be mentioned, since the index of each row is common information.  The contents of a disclosure are represented graphically in Fig.~\ref{fig:disclosure}., and two example disclosures drawn from reference databases can be found in the supporting information .

A disclosure containing these six elements satisfies most of the requirements established at the top of this section (the exception is ensuring the privacy of confidential data, which is treated later in the article):
\begin{itemize}
  \item The result is \textbf{computable} using Eq.~\ref{eqn:study};
  \item the computation is \textbf{complete} and \textbf{minimal} because all components are required and no superfluous components are included;
  \item The results are \textbf{reproducible} if the reader is able to accurately interpret the author's references in \ref{itm:bg} and \ref{itm:em};
  \item The disclosure includes only information for which the author can claim \textbf{authority};
  \item The disclosure includes all information specific to the study, or for which the study is the \textbf{primary} source, including re-implementations of already-published data. 
\end{itemize}
As mentioned, the proper interpretation of the disclosure requires that the reader accurately interprets the author's references to background databases and elementary flows, including mutually consistent implementation of the LCIA vector $\mathbf{e}$.  These aspects are out of scope for the purposes of this paper, and we will assume that a shared understanding between author and reader can be reached.  However, the challenges of operationalizing this requirement are complex (see the discussion and supporting information).  %Some implications on the information required for a successful disclosure are considered in the Discussion.

>>>>

The foreground matrix $A_f$, dependency matrix $A_d$, and foreground emission matrix $B_f$ now contain all study-specific information.  Assuming that the appropriate background LCIDB $B_x$, and the vector of characterization factors $\mathbf{c}$ (or their product $\mathbf{c}\times B_x$) are available and held in common between the author and the reader, then a disclosure that precisely describes $A_f$, $A_d$ and $B_f$ is sufficient to reproduce the study result, as formulated in Eq.~\ref{eqn:study}.  These three submatrices together can be considered a complete representation of the PSM.

\input{fig_disclosure}
Thus, the problem of how to disclose an LCA study design is reduced to the problem of how to communicate the contents of these submatrices accurately.  Recognizing that all three matrices are likely to be sparse (that is, that most of the entries are zero), the most efficient disclosure would be to only report non-zero entries.  A sparse matrix can be represented by a list of 3-tuples indicating (row, column, value) for each non-zero entry.  Thus, a formal disclosure of the PSM can be stated in six parts, including three lists of entities and three sets of data values:
\begin{enumerate}[label={\em d-\roman*}., ref={\em d-\roman*}]
\item\label{itm:fg} An ordered list of foreground nodes, beginning with the functional unit (rows/columns of $A_f$);
\item\label{itm:bg} An ordered list of background flows, each making reference to a particular background dataset (rows of $A_d$, mapping to columns of $B_x$);
\item\label{itm:em} An ordered list of exchanges with the environment (rows of $B_f$, mapping to entries in $\mathbf{c}$);
\item\label{itm:af} A set of 3-tuples for nonzero elements of $A_f$, in which the row and column are indices into Item~\ref{itm:fg};
\item\label{itm:ad} a set of 3-tuples for nonzero elements of $A_d$, in which the rows are indices into Item~\ref{itm:bg} and the columns are indices into Item~\ref{itm:fg};
\item\label{itm:bf} a set of 3-tuples for nonzero elements of $B_f$, in which the rows are indices into Item~\ref{itm:em} and the columns are indices into Item~\ref{itm:fg}.
\end{enumerate}
Each entity included in items \ref{itm:fg}--\ref{itm:em} describes a flow of some kind, and its unit of measure must be reported in the disclosure.
In both items~\ref{itm:bg} and~\ref{itm:em}, only rows containing non-zero entries need to be mentioned, since the index of each row is common information.  The contents of a disclosure are represented graphically in Fig.~\ref{fig:disclosure}., and two example disclosures drawn from reference databases can be found in the supporting information .

A disclosure containing these six elements satisfies most of the requirements established at the top of this section (the exception is ensuring the privacy of confidential data, which is treated later in the article):
\begin{itemize}
  \item The result is \textbf{computable} using Eq.~\ref{eqn:study};
  \item the computation is \textbf{complete} and \textbf{minimal} because all components are required and no superfluous components are included;
  \item The results are \textbf{reproducible} if the reader is able to accurately interpret the author's references in \ref{itm:bg} and \ref{itm:em};
  \item The disclosure includes only information for which the author can claim \textbf{authority};
  \item The disclosure includes all information specific to the study, or for which the study is the \textbf{primary} source, including re-implementations of already-published data. 
\end{itemize}
As mentioned, the proper interpretation of the disclosure requires that the reader accurately interprets the author's references to background databases and elementary flows, including mutually consistent implementation of the LCIA vector $\mathbf{c}$.  These aspects are out of scope for the purposes of this paper, and we will assume that a shared understanding between author and reader can be reached.  However, the challenges of operationalizing this requirement are complex (see the discussion and supporting information).  %Some implications on the information required for a successful disclosure are considered in the Discussion.

### 2018-02-07 aggregation/agg-lca-study.tex
Change $ to $

The same result can be obtained by relocating the $\mathbf{y}$ vector into an augmented $A$ matrix, augmenting the $B$ matrix with a vector of zeros, and replacing the final demand with a vector $\tilde{\mathbf{y}}$ in which the first entry is 1 and all successive entries are 0:
\begin{equation}
  \begin{array}{cc}
s =& \mathbf{e}^T\times B\times\left(I-A\right)^{-1}\times\mathbf{y} \\
 =& \mathbf{e}^{T}\times\tilde{B}\times\left(I-\tilde{A}\right)^{-1}\times\tilde{\mathbf{y}}
  \end{array}
  \label{eqn:canonical}
\end{equation}
where
$\tilde{A} = \left[\begin{smallmatrix} 0 & \mathbf{0}^T \\ \mathbf{y} & A  \end{smallmatrix}\right]$,
$\tilde{B} = [ \mathbf{0},\, B ]$, and $\tilde{\mathbf{y}} =  [ 1,\, 0,\, 0 ,\,\ldots,\, 0]^{T}$.
It can easily be shown that Eq.~\ref{eqn:canonical} holds for any $\mathbf{y}$  (A proof is provided in the electronic supporting information).  This is intuitively true because the $\tilde{\mathbf{y}}$ selects the first column of the augmented $\tilde{A}$ matrix as the ``final demand,'' but the ``direct requirements'' of that column are precisely the final demand from the prior, un-augmented $A$ matrix.

This same workflow can be repeated to build a more elaborate foreground.  For instance, a model of private vehicle travel may make use of reference processes for vehicle production and decommissioning, road maintenance, fuel retail, and a model of direct emissions from fuel combustion.  This model could occupy an additional column of $\tilde{A}$, with the coefficients for fuel combustion emissions being contained in the corresponding column of $\tilde{B}$.  A process for brewing coffee could be created in a third column that requires coffee beans, water, and electricity. Finally, a fourth column could be added that invokes the first three columns in proportion to describe the activity of traveling to a coffeeshop to work\footnote{No prizes for guessing where this passage was written.}.

@@

\input{fig_foreground}
It is currently common practice for background database maintainers to pre-compute the life cycle inventory results for their databases.  In cases where the background database is used without modification, including the contents of $A$ in $\tilde{A}$ becomes unnecessary.
Using the notation $B_x = B \times (I - A)^{-1}$ to represent the pre-computed background LCI database, %% $\tilde{A}$ can be ``flattened'' so that it no longer includes inventories for background processes.
%% Eq.s~\ref{eqn:foreground} can be recast as:
%% \begin{equation}
%%  \tilde{A}_{flat} = \left[\begin{array}{cc} 
%% A_f &  0 \\
%% A_d & 0 
%%    \end{array}\right];\;\;\;  \tilde{B}_{flat} = \left[\begin{array}{cc} B_f & B_x \end{array}\right ]
%% \label{eqn:fg_bg}
%% \end{equation}
%% The proof of the equivalency of results derived from Eq.s~\ref{eqn:foreground} and \ref{eqn:fg_bg} is provided in the supplementary materials.  In this form, the only information remaining in $\tilde{A}_{flat}$ pertains to the study foreground.  
%
%% Using the ordered matrices, 
Eq.~\ref{eqn:leontief} can be written so that the foreground matrix inversion is  performed separately from the computationally costly background computation:
\begin{equation}
s = \mathbf{e}^T \times (B_f + B_x\times A_d) \times (I - A_f)^{-1} \times \tilde{\mathbf{y}}_f
\label{eqn:study}
\end{equation}
where $\tilde{\mathbf{y}}_f$ is a canonical functional unit vector whose length is the same as the rank of $A_f$. Eq.~\ref{eqn:study} is derived in the supporting information.
Eq.~\ref{eqn:study} is visualized in Figure~\ref{fig:foreground}, with the background technology matrix $A$ subsumed into $B_x$ and replaced by an identity matrix $I$.

@@

The aggregated result can also be computed from the aggregated foreground:
\begin{equation}
\begin{array}{rl}
s & = \mathbf{e}^T \times( B_f + B_x \times A_d) \times \tilde{\mathbf{x}} \\
  & = \mathbf{e}^T \times( \tilde{\mathbf{b}}_f + B_x \times\tilde{\mathbf{a}}_d) \\
  & = \mathbf{e}^T \times( \tilde{\mathbf{b}}_f + \tilde{\mathbf{b}}_x) \\
\end{array}
\end{equation}

>>>>

The same result can be obtained by relocating the $\mathbf{y}$ vector into an augmented $A$ matrix, augmenting the $B$ matrix with a vector of zeros, and replacing the final demand with a vector $\tilde{\mathbf{y}}$ in which the first entry is 1 and all successive entries are 0:
\begin{equation}
  \begin{array}{cc}
s =& \mathbf{c}^T\times B\times\left(I-A\right)^{-1}\times\mathbf{y} \\
 =& \mathbf{c}^{T}\times\tilde{B}\times\left(I-\tilde{A}\right)^{-1}\times\tilde{\mathbf{y}}
  \end{array}
  \label{eqn:canonical}
\end{equation}
where
$\tilde{A} = \left[\begin{smallmatrix} 0 & \mathbf{0}^T \\ \mathbf{y} & A  \end{smallmatrix}\right]$,
$\tilde{B} = [ \mathbf{0},\, B ]$, and $\tilde{\mathbf{y}} =  [ 1,\, 0,\, 0 ,\,\ldots,\, 0]^{T}$.
It can easily be shown that Eq.~\ref{eqn:canonical} holds for any $\mathbf{y}$  (A proof is provided in the electronic supporting information).  This is intuitively true because the $\tilde{\mathbf{y}}$ selects the first column of the augmented $\tilde{A}$ matrix as the ``final demand,'' but the ``direct requirements'' of that column are precisely the final demand from the prior, un-augmented $A$ matrix.

This same workflow can be repeated to build a more elaborate foreground.  For instance, a model of private vehicle travel may make use of reference processes for vehicle production and decommissioning, road maintenance, fuel retail, and a model of direct emissions from fuel combustion.  This model could occupy an additional column of $\tilde{A}$, with the coefficients for fuel combustion emissions being contained in the corresponding column of $\tilde{B}$.  A process for brewing coffee could be created in a third column that requires coffee beans, water, and electricity. Finally, a fourth column could be added that invokes the first three columns in proportion to describe the activity of traveling to a coffeeshop to work.%\footnote{No prizes for guessing where this passage was written.}.

@@

\input{fig_foreground}
It is currently common practice for background database maintainers to pre-compute the life cycle inventory results for their databases.  In cases where the background database is used without modification, including the contents of $A$ in $\tilde{A}$ becomes unnecessary.
Using the notation $B_x = B \times (I - A)^{-1}$ to represent the pre-computed background LCI database, %% $\tilde{A}$ can be ``flattened'' so that it no longer includes inventories for background processes.
%% Eq.s~\ref{eqn:foreground} can be recast as:
%% \begin{equation}
%%  \tilde{A}_{flat} = \left[\begin{array}{cc} 
%% A_f &  0 \\
%% A_d & 0 
%%    \end{array}\right];\;\;\;  \tilde{B}_{flat} = \left[\begin{array}{cc} B_f & B_x \end{array}\right ]
%% \label{eqn:fg_bg}
%% \end{equation}
%% The proof of the equivalency of results derived from Eq.s~\ref{eqn:foreground} and \ref{eqn:fg_bg} is provided in the supplementary materials.  In this form, the only information remaining in $\tilde{A}_{flat}$ pertains to the study foreground.  
%
%% Using the ordered matrices, 
Eq.~\ref{eqn:leontief} can be written so that the foreground matrix inversion is  performed separately from the computationally costly background computation:
\begin{equation}
s = \mathbf{c}^T \times (B_f + B_x\times A_d) \times (I - A_f)^{-1} \times \tilde{\mathbf{y}}_f
\label{eqn:study}
\end{equation}
where $\tilde{\mathbf{y}}_f$ is a canonical functional unit vector whose length is the same as the rank of $A_f$. Eq.~\ref{eqn:study} is derived in the supporting information.
Eq.~\ref{eqn:study} is visualized in Figure~\ref{fig:foreground}, with the background technology matrix $A$ subsumed into $B_x$ and replaced by an identity matrix $I$.

@@

The aggregated result can also be computed from the aggregated foreground:
\begin{equation}
\begin{array}{rl}
s & = \mathbf{c}^T \times( B_f + B_x \times A_d) \times \tilde{\mathbf{x}} \\
  & = \mathbf{c}^T \times( \tilde{\mathbf{b}}_f + B_x \times\tilde{\mathbf{a}}_d) \\
  & = \mathbf{c}^T \times( \tilde{\mathbf{b}}_f + \tilde{\mathbf{b}}_x) \\
\end{array}
\end{equation}

### 2018-02-07 aggregation/agg-pagg.tex
Change $ to $

The $A_d$ and $B_f$ matrices are then partitioned into two components that sum to the original:
\begin{equation}\begin{aligned}
  A_d =\; & A_{d,pub} + A_{d,priv} \\
  B_f =\; & B_{f,pub} + B_{f,priv}
  \label{eqn:partition}
  \end{aligned}
  \end{equation}
This is illustrated in Fig.~\ref{fig:private}b.  Substituted back into Eq.~\ref{eqn:study}, the private portions are aggregated into a private life cycle inventory vector $\mathbf{b}_{priv}$, while the public portions remain disaggregated:
\begin{align}
  s =\; & \mathbf{e}^T\times\left((B_{f,pub} + B_{f,priv}) + B_x\times (A_{d,pub} + A_{d,priv})\right)\times\tilde{\mathbf{x}}\\
  =\; & \mathbf{e}^T\times\left((B_{f,pub} + B_x\times A_{d,pub})\times\tilde{\mathbf{x}} + \mathbf{b}_{priv}\right)\label{eqn:private}\\
  \mathbf{b}_{priv} =\; & (B_{f,priv} + B_x\times A_{d,priv})\times \tilde{\mathbf{x}}
\end{align}
Any foreground nodes that are completely contained within the private partition can be omitted from the disclosed foreground.  The aggregation result can then be included as a separate foreground node with a unit weight, and the aggregated inventory vector included as the corresponding column of $B_f$.  This is illustrated in Fig.~\ref{fig:private}c.

>>>>

The $A_d$ and $B_f$ matrices are then partitioned into two components that sum to the original:
\begin{equation}\begin{aligned}
  A_d =\; & A_{d,pub} + A_{d,priv} \\
  B_f =\; & B_{f,pub} + B_{f,priv}
  \label{eqn:partition}
  \end{aligned}
  \end{equation}
This is illustrated in Fig.~\ref{fig:private}b.  Substituted back into Eq.~\ref{eqn:study}, the private portions are aggregated into a private life cycle inventory vector $\mathbf{b}_{priv}$, while the public portions remain disaggregated:
\begin{align}
  s =\; & \mathbf{c}^T\times\left((B_{f,pub} + B_{f,priv}) + B_x\times (A_{d,pub} + A_{d,priv})\right)\times\tilde{\mathbf{x}}\\
  =\; & \mathbf{c}^T\times\left((B_{f,pub} + B_x\times A_{d,pub})\times\tilde{\mathbf{x}} + \mathbf{b}_{priv}\right)\label{eqn:private}\\
  \mathbf{b}_{priv} =\; & (B_{f,priv} + B_x\times A_{d,priv})\times \tilde{\mathbf{x}}
\end{align}
Any foreground nodes that are completely contained within the private partition can be omitted from the disclosed foreground.  The aggregation result can then be included as a separate foreground node with a unit weight, and the aggregated inventory vector included as the corresponding column of $B_f$.  This is illustrated in Fig.~\ref{fig:private}c.

### 2018-02-07 aggregation/proofs.tex
Change $ to $

Substituting this into the LCA system equation:
\begin{align}
  s =\;& \mathbf{e}^T\times \tilde{B}_{flat}\times(I-\tilde{A}_{flat})^{-1}\tilde{\mathbf{y}}\\
  =\;& \mathbf{e}^T\times \left[\begin{array}{cc} B_f & B_x \end{array}\right]\times
  \left[\begin{array}{cc} (I-A_f)^{-1} & 0 \\ A_d\times(I-A_f)^{-1} & I \end{array}\right]
  \times\left[\begin{array}{c} \tilde{\mathbf{y}}_f \\ \mathbf{0}\end{array}\right]
\end{align}
where $\tilde{\mathbf{y}}_f$ is a canonical functional unit having the same dimension as $A_f$.  Thus:
\begin{align}
s =\;& \mathbf{e}^T\times \left[\begin{array}{cc} B_f & B_x \end{array}\right]\times
 \left[\begin{array}{c} (I-A_f)^{-1}\times\tilde{\mathbf{y}}_f \\ A_d\times(I-A_f)^{-1}\times\tilde{\mathbf{y}}_f\end{array}\right]\\
 =\;& \mathbf{e}^T\times \left(B_f\times(I-A_f)^{-1}\times\tilde{\mathbf{y}}_f
 + B_x\times A_d\times(I-A_f)^{-1}\times\tilde{\mathbf{y}}_f\right)\\
 =\;& \mathbf{e}^T\times \left(B_f + B_x\times A_d\right)\times(I-A_f)^{-1}\times \tilde{\mathbf{y}}_f\\
 =\;& \mathbf{e}^T\times \left(B_f + B_x\times A_d\right)\times \tilde{\mathbf{x}}
\end{align}
thus completing the derivation.

>>>>

Substituting this into the LCA system equation:
\begin{align}
  s =\;& \mathbf{c}^T\times \tilde{B}_{flat}\times(I-\tilde{A}_{flat})^{-1}\tilde{\mathbf{y}}\\
  =\;& \mathbf{c}^T\times \left[\begin{array}{cc} B_f & B_x \end{array}\right]\times
  \left[\begin{array}{cc} (I-A_f)^{-1} & 0 \\ A_d\times(I-A_f)^{-1} & I \end{array}\right]
  \times\left[\begin{array}{c} \tilde{\mathbf{y}}_f \\ \mathbf{0}\end{array}\right]
\end{align}
where $\tilde{\mathbf{y}}_f$ is a canonical functional unit having the same dimension as $A_f$.  Thus:
\begin{align}
s =\;& \mathbf{c}^T\times \left[\begin{array}{cc} B_f & B_x \end{array}\right]\times
 \left[\begin{array}{c} (I-A_f)^{-1}\times\tilde{\mathbf{y}}_f \\ A_d\times(I-A_f)^{-1}\times\tilde{\mathbf{y}}_f\end{array}\right]\\
 =\;& \mathbf{c}^T\times \left(B_f\times(I-A_f)^{-1}\times\tilde{\mathbf{y}}_f
 + B_x\times A_d\times(I-A_f)^{-1}\times\tilde{\mathbf{y}}_f\right)\\
 =\;& \mathbf{c}^T\times \left(B_f + B_x\times A_d\right)\times(I-A_f)^{-1}\times \tilde{\mathbf{y}}_f\\
 =\;& \mathbf{c}^T\times \left(B_f + B_x\times A_d\right)\times \tilde{\mathbf{x}}
\end{align}
thus completing the derivation.
